Propositions as Sessions, Mechanically

### 2015-04-18 paper/presentation.tex
Working out how to introduce CP/GV.

there has been a lot of activity in this area producing a variety of different
session-based type systems. many systems build on top of previous work adding
more complex features such as asynchronous, polymorphic and recursive session
types. extending informal proofs is error-prone and difficult because it is
not always clear which parts of a system's metatheory is affected by a
change. a formalised system would be interesting to consider. the community
would benefit from a formalised system to aid extension and reduce likelihood
of errors in the proofs.

recent work has provided a logical foundation for understanding session
types. session types correspond to classical linear logic connectives. where
negation in the logic corresponds to the dual property of a session
type. [present example slide of the connectives in classical linear logic and
  their session type interpretation]. the formalisation i will describe today
regards this connection, the system GV/CP originally described by Phil Wadler
was the aim of this project to mechanise it. it provides a basis for further
additions and also provides some properties that may be desirable such as
deadlock freedom. the formalisation provides a means to gain more confidence
in the proofs but also assists in extending them to account for the effects of
additions.

>>>>

there has been a lot of activity in this area producing a variety of different
session-based type systems. many systems build on top of previous work adding
more complex features such as asynchronous, polymorphic and recursive session
types. extending informal proofs is error-prone and difficult because it is
not always clear which parts of a system's metatheory is affected by a
change. a formalised system would aid extension and reduce likelihood
of errors in the proofs since the theorem prover would highlight the effects

recent work has provided a logical foundation for understanding session
types. Wadler's work on the CP/GV system describes a two-tier type system with
session types. [present it on screen.what?] the process calculus CP interprets
linear logical connectives as session types and the surface functional
language GV can be translated into CP. The system enjoys freedom from
deadlock. surface language.

session types correspond to classical linear logic connectives. where negation
in the logic corresponds to the dual property of a session type. [present
  example slide of the connectives in classical linear logic and their session
  type interpretation]. the formalisation i will describe today regards this
connection, I will present work towards a formalisation of the system GV/CP
originally described by Phil Wadler was the aim of this project to mechanise
it. it provides a basis for further additions and also provides some
properties that may be desirable such as deadlock freedom. the formalisation
provides a means to gain more confidence in the proofs but also assists in
extending them to account for the effects of additions.
